\documentclass[]{deedy-resume-openfont}
\begin{document}

\lastupdated


\namesection{Ankush}{Chauhan}{ \urlstyle{same}\url{http://ankush.tech} \\
\href{mailto:achauhan4@student.gsu.edu}{achauhan4@student.gsu.edu} | 470.343.8844
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Georgia State University}
\descript{M.S. in Computer Science}
\location{Expected May 2017 | Atlanta, GA \\ Cum. GPA: 3.3}
\sectionsep
\subsection{Himachal Pradesh  \break University}
\descript{B.Tech. in Information Technology}
\location{Grad. Aug 2014 |  Shimla, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/ankush2611}{\custombold{ankush2611}} \\
LinkedIn://  \href{https://www.linkedin.com/in/ankunix}{\custombold{ankunix}} \\
YouTube://  \href{https://www.youtube.com/user/2611ankush}{\custombold{2611ankush}} \\
Quora://  \href{https://www.quora.com/profile/Ankush-Chauhan-1}{\custombold{Ankush-Chauhan-1}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Advance Computer Networks \\
Spatial \& Scientific Databases \\
Big Data Programming\\
\sectionsep
\subsection{Undergraduate}
Operating Systems \\
Artificial Intelligence + Practicum\\
Modeling \& Simulation + Practicum \\
Data Mining\\
Computer Networks\\
Unix Tools and Scripting \\
Discrete Mathematics\\
{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst) }}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming Languages}
C \textbullet{} C++ \textbullet{} C\# \textbullet{} Python \textbullet{} Java \textbullet{} Visual Basic \textbullet{} Java \textbullet{} Bash \textbullet{} R \textbullet{} Matlab \textbullet{} SQL \textbullet{} PL/pgSQL \textbullet{} Scala \textbullet{} CSS \textbullet{} Javascript \textbullet{} PHP \textbullet{} HTML5 \textbullet{} XML\\

\subsection{Web Technologies}
Cassandra \textbullet{} Nginx \textbullet{} NodeJS \textbullet{} Django \textbullet{} MongoDB \textbullet{} PostgreSQL \textbullet{}
MySQL \textbullet{} Digital Ocean \textbullet{} AWS \textbullet{} Heroku \textbullet{} WebGL \textbullet{} JQuery \textbullet{} Bootstrap\\

\subsection{Applications:}
AfterEffects \textbullet{} InDesign \textbullet{} Photoshop \textbullet{} GIMP \textbullet{} Illustrator \textbullet{} MS Office \textbullet{} Google Docs \textbullet{} Unix/Linux \textbullet{} Windows \textbullet{} OS X \textbullet{} Vi \textbullet{} Emacs \textbullet{} Eclipse \textbullet{} Git \textbullet{} \LaTeX \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Georgia State University}
\descript{| Graduate Teaching Assistant }
\location{January 2016 – Present | Atlanta, GA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Creating and grading homework and exam problems, interacting with students,
conducting recitations sessions.
\end{tightemize}
\sectionsep

\runsubsection{Tech Mahindra}
\descript{| Software Engineer}
\location{November 2014 – December 2015 | New Delhi, India}
\begin{tightemize}
\item Client - AT\&T U-verse
\begin{tightemize}
\item Verified data completeness and transformation rules for collected SNMP statistics from U-verse network nodes.
\item Integrate and communicate with onsite team members for technical and business requirements.
\item Updating and executing test cases and Scripts on Quality Center.
\item Preparing Test Plan and Test summary report
\item Attending defect call with developers for tracking defects.
\item Analyzed Business Requirement along with Application Design to form test cases.
\end{tightemize}
\end{tightemize}
\sectionsep
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Georgia State University}
\location{January 2016 – Present | Atlanta, GA}
\begin{tightemize}
\item \href{https://www.researchgate.net/publication/301701477}{High Dimensional Spatial Indexing using Space-Filling Curves}
\item \href{https://www.researchgate.net/publication/301893131}{An Offline-Content Dependency-Multi Function based Substrate Function Chaining}
\end{tightemize}
\sectionsep
\runsubsection{Himachal Pradesh University}
\location{August 2010 – July 2014 | Shimla, India}
\begin{tightemize}
\item Editing and compiling of college annual magazine Resonance using Adobe InDesign.
\item Editing and compiling Video documentary for University Anthem in Adobe After Effects.
\item Developing and managing an online coding competition platform based on LAMP, GCC \& Python.
\item A study on Differentiating Anatomies of OS Design of Linux Vs. Microsoft Windows.
\item RFID based Library Management System for the HP University Library.
\item Designing a video documentary for college tech fest in Adobe After Effects.
\item Developing a paint application and a game using Allegro Game Library for C/C++.
\end{tightemize}
\sectionsep
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Awards} 
\begin{tabular}{rll}
2016	     & 1\textsuperscript{st} Place  & hackGSU Spring\\
2016	     & 1\textsuperscript{st} Place  & CodeDay ATL Spring\\
2009	     & Nationals  & CBSE National Level Science Exhibition\\



\end{tabular}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}